---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# freqdistributionNogives

<!-- badges: start -->
<!-- badges: end -->

The goal of freqdistributionNogives is to automate the process of GROUPED FREQUENCY DISTRIBUTION data-framing and cumulative frequency graph.

## Installation

You can install the development version of freqdistributionNogives like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(freqdistributionNogives)
lowerlimits=c(0,5,10,15,20,25)
upperlimits=c(5,10,15,20,25,30)
frequencies=c(124,153,454,234,531,91)
basicfreqdist(lowerlimits,upperlimits,frequencies)
## basic example code
```


```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
barplot(frequencies)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
